### 2020-08-18 Analysis/Code/Paper.Rmd
Updated R to 4.0.2, and then updated the packages in packrat

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  latex_document:
    #keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true

@@

```{r cache = F}
knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
knitr::opts_chunk$set(fig.pos = "h", out.extra = "", fig.align = "center")

>>>>

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption:
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true

@@

```{r cache = F, include = F}
# Load libraries 
library(here)
library(devtools) # for installing packages through GitHub, needed for starpolishr
library(data.table)
library(stringr)
library(stringi) # that is wasteful, but it happened
library(anytime)
library(dplyr)
library(magrittr)
library(fastDummies)
library(kableExtra)
library(ggplot2)
library(ggthemes)
library(ggridges)
library(ggpubr)
library(sandwich)
library(lmtest)
library(plm)
library(stargazer)
library(starpolishr) # install by devtools::install_github("ChandlerLutz/starpolishr")
library(texreg)
library(R.utils)

knitr::opts_chunk$set(echo=F,eval=T,message=F,warning=F,comment=NA,cache=T)
knitr::opts_chunk$set(fig.pos = "hp", out.extra = "", fig.align = "center")
